### 2020-02-02 ChapterConclusion/chapterConclusion.tex
Updated: More in Future Work

>>>>

Experiments in this study have focused on performance and correctness of AP. Further experiments could be carried out to measure bandwidth requirements of AP in different scenarios as well as the effect of reduced bandwidth on both performance and correctness.

More scenarios could be tested for performance. This study has tested the performance of AP with a $0.5$ ratio of objects near and far from the boundary. Performance is expected to be best when all objects are far from the boundary as almost no message exchange is required between servers, likewise performance is expected to be worst when all objects are near to the boundary and are both `awake' and moving, as this requires the most amount of message exchange and subsequently the highest demand of both network resources and computational overhead from the algorithms used in AP. Investigating different ratios of objects near and far from the boundary, different numbers of moving and `sleeping' objects, or simply an increasing number of objects near the boundary, would determine at what point and under what circumstances AP becomes no longer scalable.
